---
title: "KruyChandara"
output: pdf_document
---
# 1 Write a R code to Generate 6X6 matrix (A) using the random numbers between 1 to 100 generate another 6x6 matrix (B) using random numbers between 500 to 600
```{r}
matrixA = sample(1:100, 36, replace=FALSE)
matrixB = sample(500:600, 36, replace=FALSE)

# set dimension of matrix
dim(matrixA) = c(6, 6)
dim(matrixB) = c(6, 6)
matrixA
matrixB
```

## A. find the range of matric A & B
```{r}
range(matrixA)
range(matrixB)
```
## B. find the max value of each row
```{r}
# Loop over my_matrix
for(row in 1:nrow(matrixA)) {
    print(max(matrixA[row,]))
    print(max(matrixB[row,]))
}
```

## C. Find the diagonal values of matrices A&B.
```{r}
diag(matrixA)
diag(matrixB)
```
## D. Multiply matrices A and B.
```{r}
matrixA %*% matrixB
```

## E.Replace the 4th row of Matrix A with diagonal values of matrix B
```{r}
matrixA[4,] = diag(matrixB)
matrixA
```
## F.Multiply matrices A &amp; B and store the values on X.
```{r}
X = matrixA %*% matrixB
X
```
## G.Divide the matrix A with matrix B. 
```{r}
d = matrixA %/% matrixB
d
```

# 2. Create a table using dataframe/tibble with the following categories(a to f) (10 marks)
```{r}
first_name_sample = c("Dara", "Chris", "Richard", "Chhay", "Tong", "Teng", "Zorn", "Vorn", "Jin", "Joy")
occ_name_sample = c("Docter", "Nurse", "Student", "Student", "Student", "Student", "Student", "Student", "Student", "Student")
place_name_sample = c("PP", "KPC", "KTS", "New York", "PP", "PP", "PP", "PP", "PP", "PP")
second_name_sample = first_name_sample[10:1]
sample_dt<-data.frame(first_name=first_name_sample, second_name=second_name_sample, age=18:27, occupation=occ_name_sample, place=place_name_sample, random_number=sample(1:100, 10, replace=FALSE))
sample_dt
# g. extract last column
last_column = sample_dt[,6]
# h. find sum and mean
sum(last_column)
mean(last_column)
```
# 3. Create a .txt file (Minimum : 150 words) with the latest news (In English) in cambodia from the official news agency’s website(Note: Include the reference link) and do the following

```{r}
# a. read text file
text = read_file(paste(getwd(), "/text.txt", sep=""))
text

# b. perofrm tokenizatin and count word
library(tidytext) # for tokenization
library(ggplot2) # for graph visualization
library(dplyr)

dataset <- data.frame(Text=text)%>% 
  unnest_tokens(Info, Text) %>%
  count(Info, sort=TRUE) # plot the graph using ggplot2

# c. Identify the most repeated word and replace that word with “KIT”
arr_dt = arrange(dataset, desc(n))
most_repeat = arr_dt[1,]
most_repeat
replace_kit = sub(most_repeat[1,][,1], "KIT", text)
replace_kit

# d. Perform the sentiment analysis

library(sentimentr)
sen1 = sentiment(text) # To know number of sentences and words(Sentiment at the sentence level)
print(sen1)
sen2 = sentiment_by(text) # total number of words 
print(sen2)
sen3 = get_sentences(text) # To display the sentences
print(sen3)
sen4<- emotion(text) # Emotion at the sentence level
print(sen4)
sen5<- emotion_by(text) # Aggregated emotion by group(s)
print(sen5)
sen6<- profanity(text) # Profanity at the sentence level
print(sen6)
sen7<- profanity_by(text) # Aggregated profanity by group(s)
sen7

# e. Plot graph
graph = data.frame(Text=text)%>% 
  unnest_tokens(Info, Text) %>%
  count(Info, sort=TRUE)  %>% 
  ggplot(aes(n, Info)) + geom_col() +
  xlab("Number of words") +
  ylab("List of word") +
  ggtitle("Text mining using R") +
  theme(axis.title.x=element_text(size=10, color="blue", face="bold", margin=margin(t=20)),
        axis.title.y=element_text(size=10, color="red", face="bold", margin=margin(r=20)),
        plot.title=element_text(size=25, color="yellow", face="bold", margin=margin(b=20)))
graph
```
# 4. Find data set from link and do
```{r}
# a.import and clean data
data <- read.csv("https://raw.githubusercontent.com/fivethirtyeight/data/master/drug-use-by-age/drug-use-by-age.csv")
data
clean_data <- lapply(data, function(x) { 
  x[is.na(x)] <- mean(x, na.rm = TRUE)
  x
})
clean_data

# b.define x and y
# x should be number of age and y should be the number of alcohol use or any other drugs because that we can analyse about the reason why people at which age are addicted to what drug and
# that might lead to solution of preventing addiction.

# c. plot graph
gph_col = ggplot(data, aes(x=age, y=alcohol.use)) +
  xlab("Age") +
  ylab("Alcohol use") +
  geom_col()+
  ggtitle("Alcohol use on age") +
  geom_smooth(method="lm") +
  theme(axis.title.x=element_text(size=10, color="blue", face="bold", margin=margin(t=20)),
        axis.title.y=element_text(size=10, color="red", face="bold", margin=margin(r=20)),
        plot.title=element_text(size=25, color="yellow", face="bold", margin=margin(b=20)))
gph_col
gph_lm = ggplot(data, aes(x=age, y=alcohol.use))  +
  xlab("Age") +
  ylab("Alcohol use") +
  geom_point(size=3, alpha = 1/3) +
  ggtitle("Alcohol use on age") +
  geom_smooth(method="lm") +
  theme(axis.title.x=element_text(size=10, color="blue", face="bold", margin=margin(t=20)),
        axis.title.y=element_text(size=10, color="red", face="bold", margin=margin(r=20)),
        plot.title=element_text(size=25, color="yellow", face="bold", margin=margin(b=20)))
gph_lm
ggsave(filename="kruychandaragraph_point.png", units="cm", width=25, height=25)


```












